Numerical trajectory patterns of floating macroalgae

### 2020-09-28 thesis_chapter_3.Rmd
added script for 2dhistogram and heatmaps

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  html_document:
  word_document:
    reference_docx: markdown/thesis_template.docx
  pdf_document:
    fig_caption: yes
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

@@

@@

## Windage

In order to calculate the direct effect of wind-drag on the kelp the wind velcocity is needed, which can be estimated by the surface-current velocity.

```{r}

p_particle <- tidync("OceanParcels/trajectory_data/PassiveFloat.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2002-01-01 00:00:00"))

p_particle_mean <- p_particle %>% 
   group_by(t) %>% 
   summarise_all(funs(mean = mean, sd = sd, min = min, max = max), na.rm = T)

p_particle$type <- "passive" # add extra column 'type' to dataframe and assigned 'passive' label

k_particle <- tidync("OceanParcels/trajectory_data/KelpFloat.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2002-01-01 00:00:00"))

k_particle_mean <- k_particle %>% 
   group_by(t) %>% 
   summarise_all(funs(mean = mean, sd = sd, min = min, max = max), na.rm = T)

k_particle$type <- "kelp" # add extra column 'type' to dataframe and assigned 'kelp' label

total_data <- rbind(p_particle, k_particle)

```{r}

plot_A <- ggplot(data = p_particle, aes(x = lon, y = lat)) + 
  geom_point() + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  theme_bw()

plot_B <- ggplot(data = k_particle, aes(x = lon, y = lat)) + 
  geom_point() + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  theme_bw()

```{r}

library(ggpubr)
ggarrange(plot_A,plot_B, labels = c("A","B"))

>>>>

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  word_document:
    reference_docx: markdown/thesis_template.docx
  html_document:
  pdf_document:
    fig_caption: yes
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

## Wind model

The characteristics of the underlying numerical wind model will be explained here...

@@

## Wind drag

```{r data, message=FALSE, warning=FALSE, include=FALSE}

p_RK4 <- tidync("OceanParcels/trajectory_data/PassiveFloat.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2002-01-01 00:00:00"))

p_RK4_mean <- p_RK4 %>% # summarise data based on time 
   group_by(t) %>% 
   summarise_all(funs(mean = mean, sd = sd, min = min, max = max), na.rm = T)

p_RK4$type <- "RK4" # add extra column 'type' to dataframe and assigned 'passive' label

k_app1 <- tidync("OceanParcels/trajectory_data/KelpFloatApp1.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2002-01-01 00:00:00"))

k_app1_mean <- k_app1 %>% # summarise data based on time 
   group_by(t) %>% 
   summarise_all(funs(mean = mean, sd = sd, min = min, max = max), na.rm = T)

k_app1$type <- "Approach 1" # add extra column 'type' to dataframe and assigned 'kelp' label

k_app2 <- tidync("OceanParcels/trajectory_data/KelpFloatApp2.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2002-01-01 00:00:00"))

k_app1_mean <- k_app2 %>% # summarise data based on time 
   group_by(t) %>% 
   summarise_all(funs(mean = mean, sd = sd, min = min, max = max), na.rm = T)

k_app2$type <- "Approach 2" # add extra column 'type' to dataframe and assigned 'kelp' label

total_data <- rbind(p_RK4, k_app1, k_app2)

```{r plots, message=FALSE, warning=FALSE, include=FALSE}

## 2D histogram plots of number of particles

bin_RK4 <- ggplot(p_RK4, aes(x=lon, y=lat)) +
  geom_bin2d(bins = 20) +
  scale_fill_continuous(type = "viridis") +
  coord_fixed() +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

bin_APP1 <- ggplot(k_app1, aes(x=lon, y=lat)) +
  geom_bin2d(bins = 20) +
  scale_fill_continuous(type = "viridis") +
  coord_fixed() +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

bin_APP2 <- ggplot(k_app2, aes(x=lon, y=lat)) +
  geom_bin2d(bins = 20) +
  scale_fill_continuous(type = "viridis") +
  coord_fixed() +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

## Heatmaps of study domain, use previous data for study site map and histograms

heatmap_RK4 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_bin2d(data = k_app1, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_APP1 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_bin2d(data = k_app1, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_APP2 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

## Scatterplots

total_traj <- ggplot(data = total_data, aes(x = lon, y = lat, colour = type)) + 
  geom_point() + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  theme_bw() +
  guides(colour=guide_legend(title="Particle type"))

library(ggpubr)
plot(total_traj)
ggarrange(heatmap_RK4,heatmap_APP1, heatmap_APP2, labels = c("A","B","C"), common.legend = TRUE, legend = c("right"))

@@
